Parsing Postfix log files

### 2008-05-23 doc/logparser-other-parsers-review.tex
Minor formatting changes to table.

\begin{table}[ht]
\begin{tabular}{l|l|l|l|l|l}
    Parser         & Parsed     & Data        & Custom        & Documentation? & Source \\
                   & test logs? & store?      & reports?      &                & code?  \\
    \hline         &            &             &               &                &        \\
    Pflogsumm      & Yes        & No          & Partial\dag   & Good           & Yes    \\
    Sawmill        & Yes        & Yes         & Searches      & Reasonable     & No     \\
    Splunk         & Yes        & Yes         & Searches      & Abundant       & No     \\
                   &            &             & \& reports    & but poor       &        \\
    Isoqlog        & No         & Yes         & No            & No             & Yes    \\
    AWStats        & Partially  & Yes         & Partial\dag   & Good           & Yes    \\
    Throughput     & N/A        & No          & No            & Brief but      & Yes    \\
    \tab{}monitor  &            &             &               & good           &        \\
    Anteater       & No         & No          & No            & No             & Yes    \\
    YAALA          & No         & Yes\ddag    & Searches      & Poor           & Yes    \\
    Lire           & Yes        & Yes         & Yes           & Yes            & Yes    \\
    Logrep         & No         & Yes         & No            & Barely         & Yes    \\
    \LMA{}         & No         & Yes         & No            & No             & Yes    \\ 
    \parsername{}  & Yes        & Yes\dag\dag & No            & Yes            & Yes    \\
\end{tabular}

>>>>

\begin{table}[ht]
\begin{tabular}{l|l|l|l|l|l}
    Parser         & Parsed test & Data        & Custom        & Documentation  & Source \\
                   & log files?  & store?      & reports?      & quality?       & code?  \\
    \hline         &             &             &               &                &        \\
    Pflogsumm      & Yes         & No          & Partial\dag   & Good           & Yes    \\
    Sawmill        & Yes         & Yes         & Searches      & Reasonable     & No     \\
    Splunk         & Yes         & Yes         & Searches      & Abundant       & No     \\
                   &             &             & \& reports    & but poor       &        \\
    Isoqlog        & No          & Yes         & No            & No             & Yes    \\
    AWStats        & Partially   & Yes         & Partial\dag   & Good           & Yes    \\
    Throughput     & N/A         & No          & No            & Brief but good & Yes    \\
    \tab{}monitor  &             &             &               &                &        \\
    Anteater       & No          & No          & No            & No             & Yes    \\
    YAALA          & No          & Yes\ddag    & Searches      & Poor           & Yes    \\
    Lire           & Yes         & Yes         & Yes           & Yes            & Yes    \\
    Logrep         & No          & Yes         & No            & Barely         & Yes    \\
    \LMA{}         & No          & Yes         & No            & No             & Yes    \\ 
    \parsername{}  & Yes         & Yes\dag\dag & No            & Yes            & Yes    \\
\end{tabular}
